---
title: "R Charts - Line, Bar, Stacked Bar"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(ggplot2)
library(dplyr)
library(plotly)
#install.packages("webshot")
#webshot::install_phantomjs()
```

## Charts, Charts, and More Charts
Get the data.

```{r cars}
postage_xl <- read_xlsx('../data/us-postage.xlsm')
obama_xl <- read_xls('../data/obama-approval-ratings.xls')
hotdog_winners <- read_xlsx('../data/hotdog-contest-winners.xlsm')
```

## Line Chart
Pretty simple, using ggplot.

```{r}
line_base <- ggplot(data=postage_xl, aes(x=Year, y=Price)) 
line <- line_base + geom_line() + geom_point()
print(line)
```

## Bar Chart

```{r}
plot <- ggplot(obama_xl, aes(Issue, Approve))
plot + geom_bar(stat = 'identity', aes(fill=Issue), position='dodge') +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
```

## Stacked Bar
Was more difficult to get multiple values (as columns) to stack, but plotly made is very simple.

```{r}
plot_ly(obama_xl, x=~Issue, y=~Approve, type='bar', name='Approve') %>%
  add_trace(y=~Disapprove, name='Disapprove') %>%
  add_trace(y=~None, name='None') %>%
  layout(yaxis = list(title='Score'), barmode='stack')
```

The last piece of code generated the stacked bar chart, but plotly produces HTML. To make the output easy to read, I kept it in Word and simply added the image after the fact.

## Pie Chart
This was hard in ggplot, but very simple using the base R library.

```{r}
winners_by_ctry <- hotdog_winners %>% group_by(hotdog_winners$Country) %>% tally()
slices <- winners_by_ctry$n
labels <- winners_by_ctry$`hotdog_winners$Country`
pct <- round(winners_by_ctry$n / sum(winners_by_ctry$n) * 100)
labels <- paste(labels, pct)
labels <- paste(labels, '%', sep='')
pie(slices, labels = labels, col=rainbow(length(labels)), main='Hot Dog Winners by Country')
```