---
title: "Tree, Area, Stacked Area, Step"
author: "Frank Neugebauer"
date: "6/27/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.height=5, fig.width=7)
```

## Tree Maps, Area Charts, Stacked Area Charts, & Step Charts

```{r}
library(readxl)
library(ggplot2)
library(dplyr)
library(plotly)
library(treemap)
```

## Load the Data

```{r}
expenditures <- read.csv('./ex2-2/expenditures.txt', sep='\t')
unemployment <- read.csv('./ex2-2/unemployement-rate-1948-2010.csv')
postage <- read_xlsx('./ex2-2/us-postage.xlsm')
population <- read_xlsx('./ex2-2/world-population.xlsm')
```

## Tree Map
A very cool visualization and not hard to put together. Especially good at quantifying categorical data.

```{r}
treemap(expenditures, 
        index=c("category"),
        vSize = "expenditure",  
        type="index", 
        palette = "Greens",  
        title="Expenditures Tree Map", 
        fontsize.title = 14)
```

## Area Chart
Pretty simple in R
```{r}
plot <- ggplot(postage, aes(x=Year, y=Price), fill=Price) +
  geom_area(fill='red') + theme_bw() + ggtitle('Postage Price 1991-2010')
print(plot)
```

## Stacked Area Chart
Unlike Tableau, I like the default ordering for the stacked area chart using the same expenditure data.

```{r}
plot <- ggplot(expenditures, aes(x=year, y=expenditure, fill=category)) +
  geom_area() + ggtitle('Expenditures Stacked Area Chart')
print(plot)
```

## Step Chart
Very straightforward using R.

```{r}
plot(unemployment$Year, unemployment$Value, type='s', col='red', xlab='Year', 
     ylab='Unemployment %', main="Unemployment by Year 1948-2010")
```